\begin{enumerate}
    \item \textbf{Music Skills and Language Learning}
    \begin{itemize}
        \item Overview and analysis of significant papers demonstrating how music skills can enhance language learning.
    \end{itemize}
    
    \item \textbf{Measuring the Impact}
    \begin{itemize}
        \item Discussing the complexities in measuring the impact of music skills on language learning.
        \item Variation in music experiences:
        \begin{enumerate}
            \item Music background.
            \item Discrimination in music.
            \item Music production skills.
        \end{enumerate}
    \end{itemize}
    
    \item \textbf{Music Skills and Speech Cues}
    \begin{itemize}
        \item Exploring the relationship between music skills and perception of speech cues.
        \item Case studies:
        \begin{enumerate}
            \item Mandarin and pitch correlation.
            \item Impact on languages with specific phonetic characteristics like Japanese and Italian, focusing on geminates.
        \end{enumerate}
    \end{itemize}
    
    \item \textbf{Methods}
    \begin{itemize}
        \item Methodological framework of the study.
        \item Participants: Detailed profile of the 38 participants.
    \end{itemize}
    
    \item \textbf{Tasks and Assessments}
    \begin{itemize}
        \item Description of various tasks and assessments used in the study:
        \begin{enumerate}
            \item Working Memory Assessment.
            \item MET Task:
            \begin{itemize}
                \item Rhythm Analysis.
                \item Melody Analysis.
            \end{itemize}
            \item Goldsmith Tasks:
            \begin{itemize}
                \item Emotion Recognition.
                \item Other relevant tasks.
            \end{itemize}
        \end{enumerate}
    \end{itemize}
\end{enumerate}